% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Tianhao Xu}

\basicInfo{
  \email{kylexu2410@gmail.com} \textperiodcentered\ 
  \phone{(+65) 86199973} \textperiodcentered\ 
  \linkedin[kyx2410]{www.linkedin.com/in/kyx2410}}

  \section{\faUsers\ Experience}
  \datedsubsection{\textbf{THOUGHTWORKS} Chengdu, China -> Singapore}{2020 -- 2022.11 -- Present}
  \role{Software Developer}
  
  \textbf{Project: Our Marriage Journey}
  Objective: An initiative aimed at providing a modernized, one-stop marriage registration service for all residents of Singapore.
  \begin{itemize}
    \item \textbf{Role \& Responsibilities}: As a full-stack developer, I primarily focused on frontend development, being a core contributor to the project's frontend aspects.
    \item \textbf{Technologies \& Implementation}:
      \begin{itemize}
        \item Utilized React and TypeScript for frontend development.
        \item Leveraged Kotlin and SpringBoot for backend processes.
        \item Deployed the application using container solutions like Docker and managed CI/CD processes and image repositories through Gitlab and Bitbucket.
        \item Managed logs using AWS tools, specifically CloudWatch.
        \item Achieved significant performance enhancements through frontend code splitting, lazy-loading of images, and CDN integrations.
      \end{itemize}
    \item \textbf{Challenges \& Solutions}:
      \begin{itemize}
        \item \textbf{Payment Integration}: Given Singapore's diverse payment landscape, eNETS was chosen as the payment gateway. Collaborated closely with the financial team to ensure a secure and user-friendly integration process.
        \item \textbf{Performance Optimization}: As user traffic grew, a noticeable increment in load times was detected. By employing frontend code splitting, database query optimizations, and the integration of CDN, we achieved a 40\% reduction in average page load times.
        \item \textbf{Data Security}: Handling sensitive marriage registration data called for a strong emphasis on security. Implemented end-to-end encryption strategies, utilized HTTPS for data transmission, and ensured key information was encrypted when at rest.
        \item \textbf{Responsive Design}: While not adopting a mobile-first strategy, considerable efforts were put into mobile adaptation and testing to ensure seamless user experiences across various devices.
        \item \textbf{Team Collaboration}: As part of the team, I actively participated in daily stand-ups and various agile practices, ensuring effective communication and alignment of project goals.
      \end{itemize}
  \end{itemize}
  
% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: TypeScript == JavaScript >= Python > Java == Kotlin
  \item Frontend: React, Vue.js, HTML, CSS (Sass, CSS-in-JS, CSS Modules), TypeScript, Jest, Cypress
  \item Backend: Familiarity with Java/Kotlin and Spring Boot from personal projects
  \item Tools \& Frameworks: Webpack, Rollup, Vite, Storybook, Lighthouse, Swagger
  \item Web Security: XSS, CSRF, SQL Injection, HTTPS, JWT
  \item Development Environments: Linux, macOS, Windows; JetBrains Suite, VSCode
  \item Dev Practices: Agile methodologies, Git, CI/CD
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Hong Kong Bapitist University (HKBU)}, Hong Kong}{2019 -- 2020}
\textit{M.S.} in Advanced Information Systems (Merit)
\datedsubsection{\textbf{Chengdu University of Information Technology}, Chengdu, China}{2013 -- 2020}
\textit{M.S.} in Computer Technology

\textit{B.Eng.} in Microelectronics Science and Engineering

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Certificate of Participation}, Southeast Asia HackGPTW}{2023}
\datedline{\textit{Merit-based Scholarship}, Hong Kong Bapitist University}{Sep 2020}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/xxxxxthhh
  \item Languages: English - Fluent, Mandarin - Native speaker
  \item AI Tools \& Technologies: Proficient with Co-pilot, chatGPT, and other AI-enhanced development tools.
  \item Data Analysis: Skilled in using Python for data analysis and visualization, with experience in libraries such as Pandas, Matplotlib, and Seaborn.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
