\documentclass{resume}
\RequirePackage{setspace}

\begin{document}
\onehalfspacing
\pagenumbering{gobble}

\name{Tianhao Xu}

\basicInfo{
  \email{kylexu2410@gmail.com} \textperiodcentered\ 
  \phone{(+65) 86199973} \textperiodcentered\ 
  \linkedin[kyx2410]{https://www.linkedin.com/in/kyx2410}}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{THOUGHTWORKS} Chengdu, China -> Singapore}{2020 -- 2022.11 -- Present}
\role{Software Developer}

Project: \textbf{One-Stop Marriage Registration Platform}
Objective: A modernized platform designed to simplify marriage registration processes for residents.
\begin{itemize}
  \item Led the frontend development using \textbf{React}, \textbf{TypeScript}, and \textbf{NextJS}. Focused on creating responsive user interfaces through mobile-first design. Optimized rendering performance by implementing advanced techniques, including asynchronous loading and reducing network requests per page.
  \item Enhanced application performance by 30\% through the effective use of \textbf{Vite}, including techniques such as code splitting, lazy-loading, and CDN optimizations, achieving a 25\% faster site speed.
  \item Collaborated closely with UX/UI designers, product managers, and backend developers. Successfully reduced integration issues by 15\%, ensuring seamless functionality and user experience.
\end{itemize}

Project: \textbf{Trust Management System Maintenance and Feature Enhancement}
Objective: To ensure system stability, meet maintenance phase SLA requirements, and implement new features and reports for enhanced business analysis and account reconciliation.
\begin{itemize}
  \item Solely responsible for the development and maintenance of the reporting feature, including designing APIs to fetch and decrypt sensitive data, reducing query time by 20\% with direct SQL queries using \textbf{PostgreSQL}.
  \item Took on multiple roles from business analysis and requirement gathering to implementation, testing, and deployment. Successfully delivered project milestones on time, showcasing strong project management and execution skills.
  \item Utilized \textbf{Kubernetes} and \textbf{AWS} to enhance system stability and scalability.
  \item Delivered complex business report requirements successfully. Automated the report generation process using scripting and scheduling tools, reducing manual effort by 40\%, demonstrating significant autonomy and problem-solving capabilities.
  \item Participated in daily agile practices. Successfully reduced sprint planning time by 20\%, ensuring team alignment and project progress.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Advanced Frontend Technologies}: React, Next.js, TypeScript, JavaScript, HTML5, CSS3
  \item \textbf{Web Performance Optimization Tools}: Vite, Webpack, Lighthouse
  \item \textbf{Frontend Testing Tools}: Jest, Cypress
  \item \textbf{Version Control \& Collaboration Tools}: Git, Agile methodologies, CI/CD
  \item \textbf{Web Security Protocols and Practices}: XSS, CSRF, HTTPS, JWT
  \item \textbf{DevOps and Cloud Technologies}: Kubernetes, Docker, AWS related 
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Hong Kong Baptist University (HKBU)}, Hong Kong}{2019 -- 2020}
\textit{M.S.} in Advanced Information Systems (Merit)
\datedsubsection{\textbf{Chengdu University of Information Technology}, Chengdu, China}{2013 -- 2020}
\textit{M.S.} in Computer Technology
\textit{B.Eng.} in Microelectronics Science and Engineering

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Certificate of Participation}, Southeast Asia HackGPTW}{2023}
\datedline{\textit{Merit-based Scholarship}, Hong Kong Baptist University}{Sep 2020}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: [https://github.com/xxxxxthhh](https://github.com/xxxxxthhh)
  \item Languages: English - Fluent, Mandarin - Native speaker
  \item Proficient with modern AI-enhanced development tools including Co-pilot and ChatGPT.
  \item Skilled in using Python for data analysis and visualization, with libraries like Pandas, Matplotlib, and Seaborn.
\end{itemize}

\end{document}
